---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hw04pjenyuh

<!-- badges: start -->
<!-- badges: end -->

The goal of hw04pjenyuh is to ...

## Installation

You can install the released version of hw04pjenyuh by asking me for a copy

``` r
install.packages("hw04pjenyuh")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(hw04pjenyuh)
## basic example code
```

Find the fifth element of the recursive sequence generated by (2, 4, 3):

```{r n}
myseq_n(x = c(2, 4, 3), n = 5)
```

Plot the output of the sequence generated by (2, 4, 3) for n = 3 to 9:

```{r plot, echo = FALSE}
myseq_plot(data.frame(2, 4, 3, 3:9))
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
